### 2021-06-13 conditions.Rmd
data cleaning scripts

---
title: "data cleaning logs"
author: "Evelyn"
date: "5/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# read data from excel file
library(readr)
library(tidyverse)

library(readxl)

df <- read_excel("C:/Users/Evelyn GAKINYA/Documents/2. Data cleaning/data cleaning scripts/input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx")

##df <- read_csv("input/raw_data/msna_dummy_2021-06-10.csv")

```

```{r}
df_1 <- df %>% 
        mutate(cluster_id = paste(enumeration_area,locality_code,oslo_area, sep = "")) %>% 
        dplyr::select(enumeration_area, locality_code, oslo_area,cluster_id)
head(df_1)

```

```{r}
##Flag if HH reports there is a pregnant or lactating HH member, but also no female HH members between 11 and 59 years
df <- df %>% 
  mutate(lactating_checked = case_when(preg_lactating == "yes" & ( df$hh_size_girls_11_15 == 0 & df$hh_size_girls_16_17 == 0 & df$hh_size_women_18_29 == 0 & df$hh_size_women_30_64 == 0) ~"Flagged", TRUE ~ ""))

```
```{r}

df1 <- df %>% 
            dplyr::select(lactating_checked,preg_lactating,hh_size_girls_11_15,hh_size_girls_16_17,hh_size_women_18_29,hh_size_women_30_64)
head(df1)

```

```{r}
##Flag if HH reports they (a) skipped meals, (b) ate less, (c) ran out of food, (d) did not eat or (e) did not eat at all, but also reports they were not worried about food
library(dplyr)
df <- df %>% 
  mutate(lacking_food_check = case_when( lack_enough_food == "yes" & (skipped_meals == "no" | ate_less == "no" | hungry_ddnt_eat == "no" | day_without_eating == "no")  ~ "Flagged", TRUE ~ ""))

```
```{r}
df2 <- df %>% 
        filter(lacking_food_check == "Flagged") %>% 
       dplyr::select(lacking_food_check,lack_enough_food,skipped_meals,ate_less,hungry_ddnt_eat,day_without_eating)
head(df2)
```

```{r}
##Flag if HH reports a member skipped a meal, but did not (1) eat less or (2) go without eating the whole day

df <- df %>% 
     mutate(skipped_meals_checked = case_when(skipped_meals == "yes" & (ate_less == "no" | day_without_eating == "no") ~ "Flagged", TRUE~ ""))

```
```{r}
df3 <- df %>% 
          filter(skipped_meals_checked == "Flagged") %>% 
          dplyr::select(skipped_meals_checked,skipped_meals,ate_less,day_without_eating)
df3
```

```{r}
##Flag if HH reports that a child dropped out of school as a coping strategy for a lack of food, but also reports either (1) having no children in the house or (2) having no children dropped out of school
df <- df %>% 
  mutate(childdropout_check = case_when( children_dropout == "yes" & (tot_children == 0 | dropout == 0) ~ "Flagged", TRUE~ ""))

```
```{r}
df3 <- df %>% 
          #filter(childdropout_check == "Flagged") %>% 
          dplyr::select(childdropout_check,tot_children,dropout)
head(df3)
```

```{r}
##Flag if HH reports that a child has gone to work as coping strategy for a lack of food, but also reports either 
##(1) having no children in the house or (2) having no children working

df <- df %>% 
  mutate(childlabour_check = case_when( child_labour == "yes" & (tot_children == 0 | under_18_working == "no" ) ~ "Flagged", TRUE~ ""))

```
```{r}
df4 <- df %>% 
  filter(childlabour_check == "Flagged") %>% 
        dplyr::select(childlabour_check,child_labour, tot_children, under_18_working)
df4
```

```{r}
##(1) Flag if HH reports at least one member experiencing psychosocial distress, but reports 0 for both

df <- df %>% 
  mutate(pss_check = case_when(hh_member_distress == "yes" &  (child_distress_number == 0 & adult_distress_number  == 0) ~ "Flagged", TRUE~ ""))

```
```{r}
df5 <- df %>% 
        #filter(pss_check == "Flagged") %>% 
        dplyr::select(hh_member_distress,child_distress_number,adult_distress_number,pss_check)
df5
```

```{r}
 #Flag if HH reports more children or adults experiencing symptoms than number of child or adult HH members
 df<-df %>% 
   mutate( no_distressed_checked = case_when( child_distress_number > tot_children | adult_distress_number > tot_adults ~ "Flagged", TRUE~ ""))

```
```{r}
df6<- df %>%
        #filter(no_distressed_checked == "Flagged") %>% 
        dplyr::select(no_distressed_checked,child_distress_number,adult_distress_number,tot_adults, tot_children)
head(df6)
```

```{r}
##if HH reports more children experiencing symptoms than number of child HH members
df<-df %>% 
   mutate( child_distressed_checked = case_when( child_distress_number > tot_children  ~ "Flagged", TRUE~ ""))
```
```{r}
df7 <- df %>% 
        #filter(child_distressed_checked == "Flagged") %>% 
        dplyr::select(child_distressed_checked,child_distress_number,tot_children)
head(df7)
```

```{r}
#Flag if HH reports more adults experiencing symptoms than number adult HH members
df<-df %>% 
   mutate( adult_distressed_checked = case_when(adult_distress_number > tot_adults ~ "Flagged", TRUE~ ""))
```

```{r}
df8<- df %>% 
     filter(grepl("^unprot", drinking_water_source)== TRUE) %>% 
  dplyr::select(drinking_water_source)
head(df8)
```

```{r}
##Flag if HH reports drinking water comes from unimproved source but domestic water comes from improved

df <- df %>% 
  mutate(drinking_water_check = case_when(grepl("^unpro", df$drinking_water_source)==TRUE & grepl("^pro", df$domestic_water_source)== TRUE ~ "Flagged", TRUE ~ ""))

```
```{r}
df9<- df %>% 
  filter(drinking_water_check == "Flagged") %>% 
  dplyr::select(drinking_water_source, domestic_water_source, drinking_water_check )
df9
```
```{r}
##Flag if HH reports that it is unsafe or neither unsafe/safe very unsafe to travel to school, but does not report any protection threats of children
##Flag also if HH identifies threats to school travel that don't match with protection threats to girls, boys, and CWDs
df <- df %>%
     mutate(safety_check = case_when(grepl("unsafe", df$school_safety) & (df$security_concerns_girls == "none" | df$security_concerns_boys == "none" | df$security_concerns_disabled == "none")~ "Flagged", TRUE ~ ""))

```

```{r}
##Flag if the number of HH member who lost their jobs  temporarily exceeds the total HH size

df <- df %>%
     mutate(covid_job_checked = case_when(df$covid_loss_job_permanent > hh_size & df$covid_loss_job_temp > df$hh_size ~ "Flagged", TRUE ~ "" ))
```
```{r}
df <- df %>%
     mutate(covid_permanent_check = case_when(df$covid_loss_job_permanent > df$hh_size ~ "Flagged", TRUE ~ "" ))
```
```{r}
df11 <- df %>% 
        #filter(covid_job_checked == "Flagged") %>% 
        dplyr::select(covid_loss_job_permanent,hh_size )
df11
```

```{r}
df <- df %>%
     mutate(covid_temporary_check = case_when(df$covid_loss_job_temp > df$hh_size ~ "Flagged", TRUE ~ "" ))
```

```{r}
##Flag if reported shelter is tent, but HH reports having defects related to windows, floors, or foundation
df <- df %>%
      mutate(tent_check = case_when(df$shelter_type_inperson == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
```
```{r}
df12 <- df %>% 
      filter(tent_check == "Flagged") %>% 
       dplyr::select(tent_check, shelter_type_inperson, shelter_issues)
head(df12)
```

```{r}
##Flag if any expenditure other than food is more than 50% of monthly expenditure
#df <- df %>%
   #mutate(expense_check = case_when( (as.numeric(df$water_exp) | as.numeric(df$rent_exp) | as.numeric(df$medical_exp) | #as.numeric(df$fuel_exp)) >= 0.5*(as.numeric(df$tot_expenses))~ "Flagged", TRUE ~ "" ))
```
```{r}
df <- df %>%
   mutate(expense_check = case_when( df$water_exp | df$rent_exp | df$medical_exp | df$fuel_exp >= 0.5*(df$tot_expenses)~ "Flagged", TRUE ~ "" ))
```

```{r}
df13 <- df %>% 
        #filter(expense_check == "Flagged") %>% 
        dplyr::select(expense_check, food_exp, water_exp,rent_exp,medical_exp,fuel_exp,tot_expenses)
head(df13)
```

```{r}
##if the number of boys working working exceeds the number of children in the household
df <- df %>%
  mutate(working_boys_checking = case_when( df$under_18_working_boys > df$tot_boys ~ "Flagged", TRUE ~ ""))
```
```{r}
##Flag if the number of girls working exceeds the number of children in the household
df <- df %>%
  mutate(working_girls_checking = case_when( df$under_18_working_girls > df$tot_girls ~ "Flagged", TRUE ~ ""))
```

```{r}
##Flag if HH report that any family members worked outside the home in past 30 days, but does not report any income from employment 
df <- df %>%
  mutate(employment_check = case_when((df$working_adults == 0 & df$under_18_working == "no") & df$primary_livelihood == "employment" ~ "Flagged", TRUE ~ ""))

```
```{r}
df15 <- df %>% 
        filter(employment_check == "Flagged") %>% 
        dplyr::select(employment_check,working_adults,under_18_working,primary_livelihood)
head(df15)
```

```{r}
##Flag if HH reports receiving cash assistance in past 30 days, but does not identify cash assistance, NGO/charity assistance, or social service
df <- df %>%
   mutate(cash_assistance_check = case_when(df$primary_livelihood == "cash_assistance" & df$aid_type != "cash" ~ "Flagged", TRUE ~ ""))
```

```{r}
df16 <- df %>% 
        filter(cash_assistance_check == "Flagged") %>% 
        dplyr::select(cash_assistance_check,primary_livelihood,aid_type)
head(df16)
```

```{r}
##flag if gender of respondent is equal to the gender of respondent in gender sensitivity question.

df <- df %>% 
    mutate(gender_check = case_when(df$gender_respondent_r == df$gender_respondent_r2 ~ "Flagged", TRUE ~ ""))
```

```{r}
df17 <- df %>% 
  filter(gender_check == "Flagged") %>% 
  dplyr::select(gender_check, gender_respondent_r, gender_respondent_r2)
df17
```
```{r}
shati
bureij
deir_balah_camp
jabalya_camp
khan_yunis_camp
maghazi
nuseirat_camp
rafah_camp

```

```{r}
##Flag if selected HH lives in Refugee camp, but municipality selected not a camp
df <- df %>% 
      mutate(camp_check = case_when(df$camp == "yes" &  (df$hh_location_gaza != "shati"| df$hh_location_gaza !="bureij" | df$hh_location_gaza != "deir_balah_camp" | df$hh_location_gaza !="jabalya_camp" | df$hh_location_gaza != "khan_yunis_camp"| df$hh_location_gaza != "maghazi"| df$hh_location_gaza != "nuseirat_camp" | df$hh_location_gaza != "rafah_camp" )~ "Flagged", TRUE ~ ""))
```
```{r}
df19 <- df %>% 
        filter(camp_check == "Flagged") %>% 
       dplyr::select(camp_check,hh_location_gaza,camp)
df19
```

```{r}
###Flag if the respondents reports going for COVID treatment, but not for COVID testing
df <- df %>% 
     mutate(covid_check = case_when( treatment_required == "covid_19_treatment"  &  treatment_required != "covid_19_testing"~ "Flagged", TRUE ~ ""))
```

```{r}
df20 <- df %>% 
      filter(covid_check == "Flagged") %>% 
     dplyr::select(covid_check,`treatment_required/covid_19_treatment`,`treatment_required/covid_19_testing`, treatment_required)
df20
```
```{r}
library(Hmisc)
df <- df %>% 
     mutate(health_barrier_check = case_when(location == "gaza" & (obstructive_barriers %nin% health_barriers) ~ "Flagged", TRUE ~ ""))
```

```{r}
df21 <- df %>% 
        filter(health_barrier_check == "Flagged") %>% 
        dplyr::select(health_barrier_check,health_barriers,obstructive_barriers,location)
head(df21)
```
```{r}
##Flag if HH Size > 20
df <- df %>% 
     mutate(hh_size_check = case_when(as.numeric(hh_size) > 20 ~ "Flagged", TRUE ~ ""))
```
```{r}
df22 <- df %>% 
        filter(hh_size_check == "Flagged") %>% 
        dplyr::select(hh_size_check,hh_size)
df22
```
```{r}
##flag if distance_hospital > 150

df <- df %>% 
      mutate(distance_check = case_when(as.numeric(distance_hospital) > 150 ~ "Flagged", TRUE ~ ""))
```

```{r}
df23<- df %>% 
        #filter(distance_check == "Flagged") %>% 
        dplyr::select(distance_check,distance_hospital)
head(df23)
```
```{r}
 ##if remote_learning == dropout
df <- df %>% 
      mutate(remote_learning_check = case_when(remote_learning == dropout ~ "Flagged", TRUE ~ ""))
```
```{r}
df24<- df %>% 
        filter(remote_learning_check == "Flagged") %>% 
        dplyr::select(remote_learning_check,remote_learning, dropout)
df24
```
```{r}
##if tot_income == 0

df <- df %>% 
      mutate(total_income_check = case_when(tot_income == 0 ~ "Flagged", TRUE ~ ""))
```
```{r}
df25<- df %>% 
        #filter(total_income_check == "Flagged") %>% 
        dplyr::select(total_income_check,tot_income)
df25
```
```{r}
##if tot_expenses == 0

df <- df %>% 
      mutate(total_expense_check = case_when(tot_expenses== 0 ~ "Flagged", TRUE ~ ""))
```

```{r}
df26<- df %>% 
        #filter(total_expense_check == "Flagged") %>% 
        dplyr::select(total_expense_check,tot_expenses)
df26
```
```{r}
##if food_exp == 0
df <- df %>% 
      mutate(food_exp_check = case_when(food_exp == 0 ~ "Flagged", TRUE ~ ""))
```

```{r}
df27<- df %>% 
        #filter(total_expense_check == "Flagged") %>% 
        dplyr::select(food_exp_check,food_exp)
df27
```
```{r}
##if water_exp == 0
df <- df %>% 
      mutate(water_exp_check = case_when(water_exp == 0 ~ "Flagged", TRUE ~ ""))
```
```{r}
df28<- df %>% 
        #filter(total_expense_check == "Flagged") %>% 
        dplyr::select(water_exp_check,water_exp)
df28
```

### 2021-06-13 data cleaning scipt.R

@@ -1,0 +1,151 @@
+library(dplyr)
+library(lubridate)
+library(readxl)
+library(kableExtra)
+library(knitr)
+library(readr)
+library(openxlsx)
+library(sf)
+library(raster)
+library(Hmisc)
+source("functions/audit_function_full.R")
+source("functions/function_handler.R")
+
+WGS84 <- crs("+init=epsg:4326")
+UTM38N <- crs("+init=epsg:32638")
+
+assessment_start_date <- as.Date("2021-05-17")
+
+# set min time and max # interviews per day
+
+time_limit <- 15
+flag_time_limit <- 30
+max_interv <- 10
+
+# read data from excel file
+##df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")
+  
+df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")
+
+###########################################################################################################
+# time check from audit files
+# today
+df$today <- as.Date(df$start, "%Y-%m-%d")
+
+df <- time_check_audit(audit_dir_path = "audit/", df,  "_uuid", time_limit = time_limit)
+
+df <- time_check(df, time_limit)
+df <- df %>% 
+  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
+                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))
+
+###########################################################################################################
+
+
+
+# when survey does not continue to hh member calculation, these surveys are not valid
+
+df <- df %>% 
+  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
+                                  TRUE ~ "no"))
+df$not_eligible
+# import loop data
+indiv_df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "member")
+
+indiv_df <- indiv_df %>%
+            mutate('_uuid' = '_submission__uuid')
+
+
+##########################################################################################
+# Deleted interviews column
+df <- df %>% 
+  mutate(
[…]

### 2021-06-13 functions/cleaning_functions.R

@@ -1,0 +1,578 @@
+kobo.xlsx.to.csv <- function(dir, sheetName, anonymise=F, anonymise_cols = NULL) {
+  files <- list.files(dir, pattern="*.xlsx")
+  parent <- read.xlsx(paste(dir,files[1],sep="/"),
+                      sheetName = sheetName)
+  child <- read.xlsx(paste(dir,files[1],sep="/"),
+                     sheetName = "member")
+  
+  
+  if (anonymise){
+    if (is.null(anonymise_cols)) {
+      anonymise_cols <- c(grep("*contact*",names(parent)), 
+                          grep("*gpslocation*",names(parent)))
+    }
+    parent_ano <- parent[,-anonymise_cols]
+    write.csv(parent_ano,paste0(dir,"/parent_anonymised.csv"), row.names = F)
+  } else {
+    write.csv(parent,paste0(dir,"/parent.csv"), row.names = F)
+  }
+  write.csv(child,paste0(dir,"/child.csv"), row.names = F)
+}
+
+anonymise.cleaned.data <- function(dir, name = NULL, anonymise_cols = NULL) {
+  name <- ifelse(is.null(name), "parent", name)
+  parent <- read.csv(sprintf("%s/%s_cleaned.csv", dir, name), stringsAsFactors = F, encoding = "UTF-8")
+  if (is.null(anonymise_cols)) {
+    anonymise_cols <- c(grep("*contact*",names(parent)), 
+                        grep("*gpslocation*",names(parent)))
+  }
+  parent_ano <- parent[,-anonymise_cols]
+  write.csv(parent_ano,sprintf("%s/%s_cleaned_anonymised.csv", dir, name), row.names = F, fileEncoding = "UTF-8")
+} 
+
+log.cleaning.change <- function(uuid, action, old.value=NULL, question.name=NULL, new.value=NULL, issue=NULL,
+                                dir) {
+  action <- ifelse(action == "c", "change", ifelse(action == "d", "deletion", ifelse(action == "f", "flag", action)))
+  if (!action %in% c("change", "deletion", "flag")) {
+    stop("action given is not a valid action")
+  }
+  if (action == "change" & (is.null(old.value) | is.null(question.name) | is.null(new.value))) {
+    stop("For a change all the parameters of old.value, question.name and new.value should be given.")
+  }
+  if (action == "flag" & is.null(question.name)) {
+    stop("For a flag the parameter question.name should be given.")
+  }
+  log_file <- sprintf("%s/cleaning_logbook.csv",dir)
[…]

### 2021-06-13 functions/setup.R

@@ -1,0 +1,28 @@
+options(java.parameters = "- Xmx1024m")
+library(cleaninginspectoR)
+library(plotKML)
+library(rgeos)
+library(xlsx)
+library(rgeos)
+library(rgdal)
+library(ggmap)
+library(raster)
+library(sf)
+library(googleLanguageR)
+library(leaflet)
+library(htmlwidgets)
+Sys.setlocale("LC_ALL","Arabic")
+WGS84 <- crs("+init=epsg:4326")
+UTM38N <- crs("+init=epsg:32638")
+
+samplepoints_file = "sample_points/samplepoints.RData"
+sampleareas_file = "sample_points/sample_areas.RData"
+load(samplepoints_file)
+load(sampleareas_file)
+samplepoints[["returnee"]] <- samplepoints[["r"]]
+sample_areas[["returnee"]] <- sample_areas[["r"]]
+
+gl_auth("test/My First Project-9df13c475b8e.json")
+
+psu <- read.csv("raw_data/combined_sample_ids.csv", stringsAsFactors = F)
+partners <- read.csv("test/partners.csv", header = F, stringsAsFactors = F)

### 2021-06-13 functions/translation.R

@@ -1,0 +1,85 @@
+#Check for each variable, if there is anything to translate, collects and extracts it for translation
+get_translations <- function(rawDF, textFieldsDF, uuid_ = "_uuid"){
+  
+  # Create empty vectors
+  question <- vector()
+  orginal_value <- vector()
+  translated_value <- NA
+  uuid <- vector()
+  #Iterates for each given columns
+  for (j in 1:nrow(textFieldsDF)) {
+    #Extracts values
+    for (rowi in 1:nrow(rawDF)){
+      value_raw <- rawDF[rowi, paste(textFieldsDF[j,])]
+      if(!is.na(value_raw)){
+        # append values to vectors
+        question <- c(question, paste(textFieldsDF[j,]))
+        orginal_value <- c(orginal_value, as.character(value_raw))
+        uuid <- c(uuid, as.character(rawDF[rowi,uuid_]))
+      }
+    }
+    # Feedback
+    cat("\014")
+    print (paste("Getting un-translated column", j, "of", nrow(textFieldsDF)))
+  }
+  
+  forTranslation <- data.frame(question, orginal_value, translated_value, uuid)
+  return(forTranslation)
+  
+}
+
+#Receives the translation and raw data set then replace all translated values with orginal values
+set_translation <- function(rawDF, translations, uuid_ = "_uuid"){
+  for (i in 1:length(rawDF)) {
+    for (j in 1:length(translations$question)) {
+      var_name <- unique(translations$question[j])
+      
+      for (r in 1:as.numeric(count(rawDF[i]))) {
+        #Compares the values and uuid
+        if (paste(var_name) == paste(translations[j, ][1]) & paste(rawDF[r, uuid_]) == paste(translations[j, ][4])) {
+          rawDF[r,var_name] <- translations[j, ][3]
+        }
+      }
+      # Feedback
+      cat("\014")
+      print (paste("Replacing translation", j, "of", length(translations$question)))
+    }
+    break()
+  }
+  return(rawDF)
+}
+
+#Iterates on all data set and looks for any non-ascii value
+check <- function(rawDF, uuid_){
+  # Create empty vectors
+  question <- NA
+  orginal_value <- NA
+  translated_value <- NA
+  uuid <- NA
+  
+  for (j in 1:length(rawDF)) {
+    #Gets the name of each variable
+    #if current column has any non-ascii value, then iterate on it
[…]

### 2021-06-13 MSNA_2021_Monitoring_report.Rmd
monitoring report

---
title: "Reach OPT MSNA 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE,comment = NA, message = FALSE, warning=FALSE, fig.align = 'center' )
```
```{r, include=FALSE}
library(dplyr)
library(lubridate)
library(readxl)
library(kableExtra)
library(knitr)
library(readr)
library(openxlsx)
library(sf)
library(raster)
library(Hmisc)
source("functions/audit_function_full.R")
source("functions/function_handler.R")

WGS84 <- crs("+init=epsg:4326")
UTM38N <- crs("+init=epsg:32638")

assessment_start_date <- as.Date("2021-05-17")

# set min time and max # interviews per day

time_limit <- 15
flag_time_limit <- 30
max_interv <- 10

# read data from excel file
##df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")

df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")

  ###########################################################################################################
# time check from audit files
# today
df$today <- as.Date(df$start, "%Y-%m-%d")

df <- time_check_audit(audit_dir_path = "audit/", df,  "_uuid", time_limit = time_limit)

# df <- time_check(df, time_limit)
df <- df %>% 
  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))

###########################################################################################################

# when survey does not continue to hh member calculation, these surveys are not valid

df <- df %>% 
  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
                                      TRUE ~ "no"))

# remove ineligible surveys
df %<>% filter(consent == "yes" & not_eligible == "no")
```
```{r,include=FALSE}
########## SAMPLE FRAMES ########################
# 
westbank_sample <- read_csv("input/sample/Final_sampling_frame_WestBank_95_9_CS 8_B 15.csv")

westbank_sample <- westbank_sample %>% 
                    rename(num_surveys = "Survey")

westbank_sample_summarized <- westbank_sample %>% 
                    group_by(gov_name) %>% 
                    summarise(num_surveys = sum(num_surveys))

gaza_sample <- read_csv("input/sample/Final_sampling_summary_Gaza.csv")

gaza_sample_summarized <- gaza_sample %>% 
                          rename(num_surveys = "# surveys") %>% 
                          group_by(Stratification) %>% 
                          summarise(num_surveys = sum(num_surveys))

east_Jerusalem_sample <- read_excel("input/sample/Final_sampling_frame_EJ_95_9_CS 5_B 15.xlsx")
ej_summarized_sample <- east_Jerusalem_sample %>% 
                        rename(num_surveys = "Survey") %>% 
                        group_by(Location) %>% 
                        summarise(num_surveys = sum(num_surveys))

```

```{r}
##########################################################################################
# Deleted interviews column
df <- df %>% 
  mutate(
    deleted = case_when(
      time_validity == "Deleted" | consent == "no" | not_eligible == "yes" ~ "yes",
      TRUE ~ "no"))

```

```{r}
########################################################################################

### Interview method

interview_method <- df %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Location = location,
         interview_type = dc_method) %>% 
 group_by(Location, interview_type) %>% tally(name = "Number_of_interviews")
interview_method
interview_method_date <- df %>% 
  dplyr::filter(today > assessment_start_date) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Location = location,
         interview_type = dc_method) %>% 
   group_by(interview_type, Date) %>% tally(name = "Number_of_interviews")
interview_method_date

library(plotly)
survey_method_graph <- plot_ly(interview_method_date, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews Per Day', type = 'scatter', mode = 'lines',
        line = list(color = 'rgb(205, 12, 24)', width = 4)) 
# interview_method Wide format
interview_method_wide <- tidyr::pivot_wider(interview_method, 
                                            names_from = interview_type, 
                                            values_from = Number_of_interviews,
                                            values_fill = list(Number_of_interviews = 0))%>% 
  dplyr::select(Location, `Face to Face` = in_person, Phone = remote )

interview_method_wide
```
```{r}
### Interview method Westbank

interview_method_wb <- df %>%
  filter(!is.na(hh_location_wb)) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Governorate = hh_location_wb,
         interview_type = dc_method
  ) %>% 
 group_by(Governorate, interview_type) %>% tally(name = "Number_of_interviews")

interview_method_wb

interview_method_date_wb <- df %>% 
  dplyr::filter(today > assessment_start_date & !is.na(hh_location_wb)) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Governorate = hh_location_wb,
         interview_type = dc_method) %>% 
   group_by(interview_type, Date) %>% tally(name = "Number_of_interviews")

interview_method_date_wb

library(plotly)
survey_method_graph_wb <- plot_ly(interview_method_date_wb, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews West Bank', type = 'scatter', mode = 'lines',
        line = list(color = 'rgb(205, 12, 24)', width = 4)) 
survey_method_graph_wb
# interview_method Wide format

interview_method_wide_wb <- tidyr::pivot_wider(interview_method_wb, 
                                            names_from = interview_type, 
                                            values_from = Number_of_interviews,
                                            values_fill = list(Number_of_interviews = 0))

survey_method_graph_wb
```

```{r}
### Interview method Gaza

interview_method_gaza <- df %>%
  filter(!is.na(hh_location_gaza)) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Municipality = hh_location_gaza,
         interview_type = dc_method
  ) %>% 
 group_by(Municipality, interview_type) %>% tally(name = "Number_of_interviews")

interview_method_gaza

interview_method_date_gaza <- df %>% 
  dplyr::filter(today > assessment_start_date & !is.na(hh_location_gaza)) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Municipality = hh_location_gaza,
         interview_type = dc_method) %>% 
   group_by(interview_type, Date) %>% tally(name = "Number_of_interviews")
interview_method_date_gaza

library(plotly)
survey_method_graph_gaza <- plot_ly(interview_method_date_gaza, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews Gaza', type = 'scatter', mode = 'lines',
        line = list(color = 'rgb(205, 12, 24)', width = 4)) 
survey_method_graph_gaza 
# interview_method Wide format
interview_method_wide_gaza <- tidyr::pivot_wider(interview_method_gaza, 
                                            names_from = interview_type, 
                                            values_from = Number_of_interviews,
                                            values_fill = list(Number_of_interviews = 0))

interview_method_wide_gaza
```
```{r}
### Interview method East Jerusalem

interview_method_EJ <- df %>%
  filter(location == "ej") %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Location = location,
         interview_type = dc_method
  ) %>% 
 group_by(Location, interview_type) %>% tally(name = "Number_of_interviews")
interview_method_EJ

interview_method_date_EJ <- df %>% 
  dplyr::filter(today > assessment_start_date & location == "ej") %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         Location = location,
         interview_type = dc_method) %>% 
   group_by(interview_type, Date) %>% tally(name = "Number_of_interviews")
interview_method_date_EJ

library(plotly)
survey_method_graph_EJ <- plot_ly(interview_method_date_EJ, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews EJ', type = 'scatter', mode = 'lines',
        line = list(color = 'rgb(205, 12, 24)', width = 4)) 
survey_method_graph_EJ
# interview_method Wide format
interview_method_wide_EJ <- tidyr::pivot_wider(interview_method_EJ, 
                                            names_from = interview_type, 
                                            values_from = Number_of_interviews,
                                            values_fill = list(Number_of_interviews = 0))
interview_method_wide_EJ

```

### 2021-06-14 Indivual_analysis.R
Data Cleaning
Data Cleaning

@@ -1,0 +1,40 @@
+indiv_df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "member")
+
+indiv_df <- indiv_df %>%
+  mutate('_uuid' = '_submission__uuid')
+#recode difficulties to 1 and 0
+
+difficulty <- c("a_lot_of_difficulty","cannot_do_at_all")
+no_difficulty <- c("no_difficulty", "some_difficulty")
+indiv_df <- indiv_df %>%
+  mutate(seeing_difficulty = case_when(difficulty_seeing %in% difficulty ~ 1,
+                                       difficulty_seeing %in% no_difficulty ~0,
+                                       TRUE~ NA_real_),
+         hearing_difficulty = case_when(difficulty_hearing %in% difficulty ~ 1,
+                                        difficulty_hearing %in% no_difficulty ~0,
+                                        TRUE~ NA_real_),
+         walking_difficulty = case_when(difficulty_walking %in% difficulty ~ 1,
+                                        difficulty_walking %in% no_difficulty ~0,
+                                        TRUE~ NA_real_),
+         remembering_difficulty = case_when(difficulty_remembering %in% difficulty ~ 1,
+                                            difficulty_remembering %in% no_difficulty ~0,
+                                            TRUE~ NA_real_),
+         washing_difficulty = case_when(difficulty_washing %in% difficulty ~ 1,
+                                        difficulty_washing %in% no_difficulty ~0,
+                                        TRUE~ NA_real_),
+         communicating_difficulty = case_when(difficulty_communicating %in% difficulty ~ 1,
+                                              difficulty_communicating %in% no_difficulty ~0,
+                                              TRUE~ NA_real_),
+         uuid = '_submission__uuid')
+
+# group indiv data and join with hh level
+indiv_analysis <- indiv_df %>% 
+  group_by(`_submission__uuid`) %>% 
+  summarise(count_seeing_difficulty = sum(seeing_difficulty,na.rm = T),
+            count_hearing_difficulty = sum(hearing_difficulty,na.rm = T),
+            count_walking_difficulty = sum(walking_difficulty,na.rm = T),
+            count_remembering_difficulty = sum(remembering_difficulty,na.rm = T),
+            count_washing_difficulty = sum(washing_difficulty,na.rm = T),
[…]

### 2021-06-14 functions/audit_function_full.R

@@ -1,0 +1,148 @@
+
+library(tidyr)
+library(dplyr)
+library(expss)
+# Audit result function
+audit_results <- function(audit_dir_path, df_raw, enumerator_code, x_uuid, today){
+  
+  audit_dir<-audit_dir_path
+  uuids<-dir(audit_dir)
+  uuid_file<-paste0(audit_dir,"\\","\\audit.csv")
+  dfl<-list()
+  all_uuids <- length(uuids)
+  
+  for(i in 1: all_uuids){
+    df <-read.csv(paste0(audit_dir, uuids[i],"/audit.csv"))
+    df$uuid <- uuids[i]
+    dfl[[i]]<- df
+    cat("\014","Running audit: ", round((i/all_uuids) * 100,0),"%", sep = "")
+  }
+
+  audit_df <- do.call("rbind", dfl)
+  audit_df$node <- sub('.*/', '', audit_df$node)
+  # only_questions <- audit_df %>% filter(node != "")
+  
+  audit_joined <- audit_df %>% 
+    left_join(dplyr::select(df_raw, enumerator_code, x_uuid, today), by = c("uuid"="_uuid"))
+  
+  audit_joined <- audit_joined %>% 
+    mutate(
+      time_seconds =  round((end - start) * 0.001,1),
+      time_minutes =  round(time_seconds / 60,2)
+    )
+  
+  other_events <- audit_joined %>% filter(event != "question")
+  only_questions <- audit_joined %>% filter(event == "question")
+  
+  return(list(question_events = only_questions, other_events = other_events))
+  
+}
+
+
+### Reports function
+audit_report_wide <- function(audit_results, enumerator_code){
+  
+  report <- audit_results %>% 
+    group_by(Enumerator_Unique_Id = .[,enumerator_code], node) %>%
+    summarise(seconds_mean = round(mean(time_seconds, na.rm = T),1)
+    )
+  
+  report_by_date <- audit_results %>% 
+    group_by(today, Enumerator_Unique_Id = .[,enumerator_code], node) %>%
+    summarise(seconds_mean = round(mean(time_seconds, na.rm = T),1)
+    )
+  
+  report_wide <- report %>%
+    dplyr::select(Enumerator_Unique_Id, node, seconds_mean) %>%
+    pivot_wider(names_from = Enumerator_Unique_Id, values_from = seconds_mean)
+  
+  report_wide_2 <- report %>%
[…]

### 2021-06-14 functions/function_handler.R

@@ -1,0 +1,179 @@
+
+compare_columns_valuesLimit_col <- function(
+  df, cn, condition, question_label, issue_label,  columns, old_value, action_label, index) {
+
+  varname <- paste("", cn , sep="")
+  data <- df %>%  
+    mutate(issue = issue_label,
+           flag_index = index,
+           log_number = 0,
+           question.name = question_label,
+           changed = NA,
+           old.value =case_when(
+             eval(
+               parse(text = condition)
+             ) ~ as.character(eval(parse(text = old_value))),
+             TRUE ~ "Okay"),
+           new.value = NA,
+           !!varname := case_when(
+             eval(
+               parse(text = condition)
+             ) ~ action_label,
+             TRUE ~ "Okay"
+           ))
+  
+  filterDate <- data %>%
+    dplyr::select(columns)  %>% 
+    filter(
+      eval(
+        parse(text =  paste("data$", cn , sep="")
+        )) == 'Flagged' | 
+        eval(
+          parse(text =  paste("data$", cn , sep="")
+          )) == 'Deleted')
+  
+  return(filterDate)
+}
+
+compare_columns_values <- function(df, cn, condition) {
+  varname <- paste("", cn , sep="")
+  
+  data <- df %>%  
+    mutate(!!varname := case_when(
+      eval(
+        parse(text = condition)
+      ) ~ "Flagged",
+      TRUE ~ "Okay"
+    ))
+
+  return(data)
+}
+
+# this function is handling datetime diffirence
+interview_time_handler <- function(df){
+  new_df <- df %>% 
+    mutate(
+      time_spend = difftime(
+        as.POSIXct(df$end, format="%Y-%m-%dT%H:%M:%OS"), 
+        as.POSIXct(df$start, format="%Y-%m-%dT%H:%M:%OS"), units='mins')
+    )
+  return(new_df)
+}
+
+# this function is handling date diffirence
+interview_date_handler <- function(df){
+  new_df <- df %>% 
+    mutate(
+      arrival_displace_date_diff = difftime(
+        as.POSIXct(df$arrival_date_idp, format="%Y-%m-%d"), 
+        as.POSIXct(df$displace_date_idp, format="%Y-%m-%d"), units='days')
+    )
+  
+  return(new_df)
+}
+
+read_conditions_from_excel_column <- function(df, conditionDf) {
+  counter <- 0
+  for (row in 1:nrow(conditionDf)) {
[…]

### 2021-06-16 conditions.Rmd
Changes to the conditions scripts

@@
 # read data from excel file
+
 library(readr)
 library(tidyverse)
-
+library(Hmisc)
 library(readxl)
 
-df <- read_excel("C:/Users/Evelyn GAKINYA/Documents/2.
-Data cleaning/data cleaning scripts/input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx")
+##df <- read_csv("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.csv")
 
 ##df <- read_csv("input/raw_data/msna_dummy_2021-06-10.csv")
+
+df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_-_all_versions_-_False_-_2021-06-16-07-13-11.xlsx")
 
@@
 ```{r}
-df_1 <- df %>% 
-        mutate(cluster_id = paste(enumeration_area,locality_code,oslo_area, sep = "")) %>% 
-        dplyr::select(enumeration_area, locality_code, oslo_area,cluster_id)
-head(df_1)
+library(dplyr)
+df_2 <- df %>% 
+          mutate(cluster_id = if_else(is.na(oslo_area),
+            paste(enumeration_area,locality_code, sep = ""),
+            paste(enumeration_area,locality_code,oslo_area, sep = ""))) %>%
+            dplyr::select(cluster_id,enumeration_area,locality_code, oslo_area )
+head(df_2)
 
+```
+
+```{r}
+library(dplyr)
+df_3 <- df %>% 
+          mutate(
+            oslo_area =replace(oslo_area,is.na(oslo_area), "gaza"),
+            cluster_id =paste(enumeration_area,locality_code,oslo_area, sep = "_")) %>%
+            dplyr::select(cluster_id,enumeration_area,locality_code, oslo_area )
+head(df_3)
 ```
@@
 df4 <- df %>% 
-  filter(childlabour_check == "Flagged") %>% 
+  #filter(childlabour_check == "Flagged") %>% 
         dplyr::select(childlabour_check,child_labour, tot_children, under_18_working)
@@
 df12 <- df %>% 
-      filter(tent_check == "Flagged") %>% 
+      #filter(tent_check == "Flagged") %>% 
        dplyr::select(tent_check, shelter_type_inperson, shelter_issues)
@@
 ##Flag if any expenditure other than food is more than 50% of monthly expenditure
-#df <- df %>%
-   #mutate(expense_check = case_when( (as.numeric(df$water_exp) | as.numeric(df$rent_exp) | as.numeric(df$medical_exp) | #as.numeric(df$fuel_exp)) >= 0.5*(as.numeric(df$tot_expenses))~ "Flagged", TRUE ~ "" ))
+df <- df %>%
+   mutate(expense_check = case_when( (as.numeric(df$water_exp) | as.numeric(df$rent_exp) | as.numeric(df$medical_exp) | as.numeric(df$fuel_exp)) >= 0.5*(as.numeric(df$tot_expenses))~ "Flagged", TRUE ~ "" ))
 ```
 ```{r}
-df <- df %>%
-   mutate(expense_check = case_when( df$water_exp | df$rent_exp | df$medical_exp | df$fuel_exp >= 0.5*(df$tot_expenses)~ "Flagged", TRUE ~ "" ))
+##df <- df %>%
+   ##mutate(expense_check = case_when( df$water_exp | df$rent_exp | df$medical_exp | df$fuel_exp >= 0.5*(df$tot_expenses)~ ##"Flagged", TRUE ~ "" ))
 ```
@@
 ```
-```{r}
-shati
-bureij
-deir_balah_camp
-jabalya_camp
-khan_yunis_camp
-maghazi
-nuseirat_camp
-rafah_camp
-
-```
 
@@
 df <- df %>% 
-      mutate(camp_check = case_when(df$camp == "yes" &  (df$hh_location_gaza != "shati"| df$hh_location_gaza !="bureij" | df$hh_location_gaza != "deir_balah_camp" | df$hh_location_gaza !="jabalya_camp" | df$hh_location_gaza != "khan_yunis_camp"| df$hh_location_gaza != "maghazi"| df$hh_location_gaza != "nuseirat_camp" | df$hh_location_gaza != "rafah_camp" )~ "Flagged", TRUE ~ ""))
+      mutate(camp_check = case_when(df$camp == "yes" &  (df$hh_location_gaza != "shati_camp"| df$hh_location_gaza !="bureij_camp" | df$hh_location_gaza != "deir_balah_camp" | df$hh_location_gaza !="jabalya_camp" | df$hh_location_gaza != "khan_yunis_camp"| df$hh_location_gaza != "maghazi_camp"| df$hh_location_gaza != "nuseirat_camp" | df$hh_location_gaza != "rafah_camp" )~ "Flagged", TRUE ~ ""))
 ```
@@
 ```{r}
-library(Hmisc)
 df <- df %>% 
@@
 ```
+
+```{r}
+##Flag if tot_cwd == 0 and drop_out_reason == "Disability"
+df <- df %>% 
+      mutate(disability_check = case_when( tot_cwd == 0 & drop_out_reason == "Disability" ~ "Flagged", TRUE ~ ""))
+```

### 2021-06-16 data cleaning scipt.R

@@ -25,7 +25,8 @@ max_interv <- 10
 # read data from excel file
 ##df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")
   
-df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")
+##df <- read_csv("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.csv")
+df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_-_all_versions_-_False_-_2021-06-16-07-13-11.xlsx")
 
 ###########################################################################################################
 # time check from audit files
@@ -121,7 +122,7 @@ deleted_surveys <- replaced_df %>%
 deleted_uuids <- deleted_surveys %>% 
   dplyr::select(`_uuid`, deleted = time_validity)
 
-###join with individual data set to remove deleted uuids from loop
+# ##join with individual data set to remove deleted uuids from loop
 indiv_df <- left_join(indiv_df, deleted_uuids, by = "_uuid") 
 
 ###take uuids of deleted loop surveys and remove from cleaned dataset
@@ -135,7 +136,10 @@ replaced_df %<>% filter(deleted == "no")
 
 ### Generating the cluster id
 #replaced_df <- replaced_df %>% 
-               #mutate(cluster_id = paste(enumeration_area,locality_code,oslo_area, sep = ""))
+#mutate(
+# oslo_area =replace(oslo_area,is.na(oslo_area), "gaza"),
+# cluster_id =paste(enumeration_area,locality_code,oslo_area, sep = "_")) %>%
+# dplyr::select(cluster_id,enumeration_area,locality_code, oslo_area )
 
 # export clean data
 write.csv(replaced_df, sprintf("output/cleaned_data/mcna_data_clean_parent_%s.csv",today()), row.names = FALSE)

### 2021-06-16 xlsformfill_dummydata.R

@@ -1,0 +1,35 @@
+# install packages required
+devtools::install_github(
+  "mabafaba/koboquest",
+  build_opts = c(), force = T)
+
+devtools::install_github(
+  "boukepieter/dclogger",
+  build_opts = c(), force = T)
+
+devtools::install_github(
+  "mabafaba/kobostandards",
+  build_opts = c(), force = T
+)
+
+devtools::install_github(
+  "mabafaba/xlsformfill",
+  build_opts = c(), force = T
+)
+
+
+
+# questionnaire
+questions <- read.csv("input/raw_data/kobo_questions.csv", 
+                      stringsAsFactors=T, check.names=T)
+colnames(questions)[1] <- "type"
+
+
+choices <- read.csv("input/raw_data/kobo_choices.csv", 
+                    stringsAsFactors=F, check.names=T)
+colnames(choices)[1] <- "list_name"
+
+dummy_data <- xlsformfill::xlsform_fill(questions, choices, 1000)
+
+
+write.csv(dummy_data, sprintf("input/raw_data/msna_dummy_%s.csv",today()), row.names = FALSE)

### 2021-06-17 Interview Duration.Rmd
Using Pilot data
1st day of the pilot survey

---
title: "MNSA PILOT DATA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r,include=FALSE}
library(dplyr)
library(lubridate)
library(readxl)
library(kableExtra)
library(knitr)
library(readr)
library(openxlsx)
library(sf)
library(raster)
library(Hmisc)
source("functions/audit_function_full.R")
source("functions/function_handler.R")

WGS84 <- crs("+init=epsg:4326")
UTM38N <- crs("+init=epsg:32638")

assessment_start_date <- as.Date("2021-06-16")

# set min time and max # interviews per day

time_limit <- 15
flag_time_limit <- 30
max_interv <- 10

df <-  read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-16-14-45-28.xlsx")

###########################################################################################################
# time check from audit files
# today
df$today <- as.Date(df$start, "%Y-%m-%d")

df <- time_check_audit(audit_dir_path = "audit/", df,  "_uuid", time_limit = time_limit)

df <- time_check(df, time_limit)
df <- df %>% 
  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))

###########################################################################################################
df$time_validity

# when survey does not continue to hh member calculation, these surveys are not valid

df <- df %>% 
  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
                                  TRUE ~ "no"))
df$not_eligible
# import loop data
indiv_df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "member")

indiv_df <- indiv_df %>%
            mutate('_uuid' = '_submission__uuid')

##########################################################################################
# Deleted interviews column
df <- df %>% 
  mutate(
    deleted = case_when(
      time_validity == "Deleted" | consent == "no" | not_eligible == "yes" ~ "yes",
      TRUE ~ "no"))
df$deleted

########################################################################################
###########################################################################################################
# calculate new variables

# number of NAs check
df$NAs <- apply(df,1,FUN=function(x){length(which(is.na(x)))})

##########################################################################################################
### EXPORT FOR DATA CHECKING #############

##df<- df %>% 
##dplyr::select(-(snowballing_willing:`_gpslocation_precision`))

##### Write to csv for data checking ###################
write.csv(df, sprintf("output/data_checking/mcna_all_data_%s.csv",today()), row.names = F)

###########################################################################################################
###########################################################################################################
###########################################################################################################
# DO CLEANING
# read cleanimg conditions csv list
conditionDf_1 <- read.csv("input/conditions/conditions_log1.csv", as.is = TRUE)

# return logs

logs <- read_conditions_from_excel_limited_row(df, conditionDf_1);

# create new columns "log_number"
logs$log_number = seq.int(nrow(logs))
# order data frame by log_number
ordered_df <- logs[order(logs$log_number),]
readr::write_excel_csv(ordered_df, sprintf("output/cleaning_log/cleaning_log_%s.csv",today()))

# export data with check columns
logs_as_columns <- read_conditions_from_excel_column(df, conditionDf_1);
write.csv(logs_as_columns, sprintf("output/cleaning_log/data_w_checks/data_checks_%s.csv",today()), row.names = FALSE)

#################################################################################################################
# read log csv file after AO has indicated decision on flagged data
log_df <- read.csv(sprintf("output/cleaning_log/cleaning_log_%s.csv",today()), as.is = TRUE)
replaced_df <- read_logs(df, log_df, conditionDf_1)

# take uuids of deleted surveys and remove from cleaned dataset
deleted_surveys <- replaced_df %>% 
  filter(deleted == "yes")

deleted_uuids <- deleted_surveys %>% 
  dplyr::select(`_uuid`, deleted = time_validity)

# ##join with individual data set to remove deleted uuids from loop
indiv_df <- left_join(indiv_df, deleted_uuids, by = "_uuid")

###take uuids of deleted loop surveys and remove from cleaned dataset
deleted_loop <- indiv_df %>% 
filter(!is.na(deleted))

indiv_cleaned <- indiv_df %>%  filter(is.na(deleted))

# remove deleted surveys from cleaned dataset
replaced_df %<>% filter(deleted == "no")

#  data collected today
today_df <- replaced_df %>% 
  filter(today == assessment_start_date)
```
**Duration of surveys**
```{r}
survey_duration <- today_df %>% 
  filter(today_df$consent == "yes") %>% 
  group_by(Enumerator = enumerator_num) %>% 
  summarise(
    Median_duration = round(median(interview_duration, na.rm = T),0)
  )
survey_duration
```
```{r}
survey_duration_2 <- today_df %>% 
  filter(today_df$consent == "yes") %>% 
  dplyr::select(enumerator_num,interview_duration)
survey_duration_2
```

```{r}
bargraph1 <- ggplot(data = survey_duration_2, aes(x=reorder(enumerator_num,interview_duration), y = interview_duration, fill= enumerator_num)) +
             geom_boxplot() +
             labs(title = "Survey duration",
                  x = "Enumerator",
                  y = "Duration")
bargraph1
```

*Surveys with less Than  30 mins*
```{r}
duration_less_30 <- today_df %>% 
  filter(today_df$consent == "yes" & interview_duration <= 30) %>% 
  dplyr::select(enumerator_num,interview_duration)
duration_less_30
```

### 2021-06-20 Interview Duration.Rmd
Last day of pilot
Data from the pilot survey

@@
 
-df <-  read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-16-14-45-28.xlsx")
+df <-  read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx")
 
@@
 # import loop data
-indiv_df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "member")
+indiv_df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "member")
 
@@
     Median_duration = round(median(interview_duration, na.rm = T),0)
-  )
+  ) %>% 
+arrange(desc(Median_duration) )
 survey_duration
@@
 
-*Surveys with less Than  30 mins*
+*Surveys with less Than  40 mins*
 ```{r}
 duration_less_30 <- today_df %>% 
-  filter(today_df$consent == "yes" & interview_duration <= 30) %>% 
+  filter(today_df$consent == "yes" & interview_duration <= 40) %>% 
   dplyr::select(enumerator_num,interview_duration)

### 2021-06-23 conditions.Rmd
Update on Cleaning and Conditions
A function for removing notes and updated condition logs

@@
 df <- df %>% 
-  mutate(childdropout_check = case_when( children_dropout == "yes" & (tot_children == 0 | dropout == 0) ~ "Flagged", TRUE~ ""))
+  mutate(childdropout_check = case_when( coping_children_dropout == "yes" & (tot_children == 0 | dropout_num == 0) ~ "Flagged", TRUE~ ""))
 
@@
 df <- df %>% 
-  mutate(childlabour_check = case_when( child_labour == "yes" & (tot_children == 0 | under_18_working == "no" ) ~ "Flagged", TRUE~ ""))
+  mutate(childlabour_check = case_when( coping_child_labour == "yes" & (tot_children == 0 | under_18_working == "no" ) ~ "Flagged", TRUE~ ""))
 
@@
 df <- df %>%
-      mutate(tent_check = case_when(df$shelter_type_inperson == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
+      mutate(tent_check = case_when(df$shelter_type == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
 ```
@@
 df <- df %>% 
-    mutate(gender_check = case_when(df$gender_respondent_r == df$gender_respondent_r2 ~ "Flagged", TRUE ~ ""))
+    mutate(gender_check = case_when(df$gender_respondent == df$gender_respondent ~ "Flagged", TRUE ~ ""))
 ```
@@
 df <- df %>% 
-      mutate(remote_learning_check = case_when(remote_learning == dropout ~ "Flagged", TRUE ~ ""))
+      mutate(remote_learning_check = case_when(remote_learning == dropout_num ~ "Flagged", TRUE ~ ""))
 ```

### 2021-06-26 data cleaning scipt.R
Adding variable "strata" in the data
Adding an entire column in the data, that is "strata

@@ -1,157 +1,0 @@
-library(dplyr)
-library(lubridate)
-library(readxl)
-library(kableExtra)
-library(knitr)
-library(readr)
-library(openxlsx)
-library(sf)
-library(raster)
-library(Hmisc)
-source("functions/audit_function_full.R")
-source("functions/function_handler.R")
-
-WGS84 <- crs("+init=epsg:4326")
-UTM38N <- crs("+init=epsg:32638")
-
-assessment_start_date <- as.Date("2021-06-16")
-
-# set min time and max # interviews per day
-
-time_limit <- 15
-flag_time_limit <- 30
-max_interv <- 10
-
-df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "MSNA_I_2021")
-
-###########################################################################################################
-# time check from audit files
-# today
-df$today <- as.Date(df$start, "%Y-%m-%d")
-
-df <- time_check_audit(audit_dir_path = "audit/", df,  "_uuid", time_limit = time_limit)
-
-df <- time_check(df, time_limit)
-df <- df %>% 
-  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
-                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))
-df_raw <- df
-write.xlsx(df_raw, (file = sprintf("output/df_raw_%s.xlsx", today())))
-
-###########################################################################################################
-df$time_validity
-
-
-
-# when survey does not continue to hh member calculation, these surveys are not valid
-
-df <- df %>% 
-  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
-                                  TRUE ~ "no"))
-df$not_eligible
-# import loop data
-indiv_df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "member")
-
-indiv_df <- indiv_df %>%
-            mutate('_uuid' = '_submission__uuid')
-
-
-##########################################################################################
-# Deleted interviews column
-df <- df %>% 
-  mutate(
-    deleted = case_when(
-      time_validity == "Deleted" | consent == "no" | not_eligible == "yes" ~ "yes",
-      TRUE ~ "no"))
-df$deleted
-
-
-
-########################################################################################
[…]

### 2021-06-26 MSNA_2021_Monitoring_report.Rmd
Changes to the conditions scripts
Update on monitoring report
Data collection monitoring report both in html and pdf.

@@
 title: "Reach OPT MSNA 2021"
-output: html_document
+output:
+  html_document: default
+  pdf_document: default
 ---
+
+<style type="text/css">
+.main-container {
+  max-width: 1800px;
+  margin-left: auto;
+  margin-right: auto;
+}
+</style>
 
@@
 
-assessment_start_date <- as.Date("2021-05-17")
+assessment_start_date <- as.Date("2021-06-16")
 
@@
 
-df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "MSNA_I_2021")
+df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "MSNA_I_2021")
 
@@
 df %<>% filter(consent == "yes" & not_eligible == "no")
-```
-```{r,include=FALSE}
+
 ########## SAMPLE FRAMES ########################
 # 
-westbank_sample <- read_csv("input/sample/Final_sampling_frame_WestBank_95_9_CS 8_B 15.csv")
+westbank_sample_df <- read_csv("input/sample/Final_sampling_frame_WestBank_95_9_CS 8_B 15.csv")
 
-westbank_sample <- westbank_sample %>% 
-                    rename(num_surveys = "Survey")
-
-westbank_sample_summarized <- westbank_sample %>% 
-                    group_by(gov_name) %>% 
+westbank_sample_df_summarized <- westbank_sample_df %>% 
+                    rename(num_surveys = "Survey") %>% 
+                    group_by(strata) %>% 
                     summarise(num_surveys = sum(num_surveys))
 
-gaza_sample <- read_csv("input/sample/Final_sampling_summary_Gaza.csv")
+#westbank_sample_df_summarized <- write.csv(westbank_sample_df_summarized, sprintf("input/sample/westbank_sample_df_summarized_%s.csv", today()), row.names = FALSE)
 
-gaza_sample_summarized <- gaza_sample %>% 
+gaza_sample_df <- read_csv("input/sample/Final_sampling_summary_Gaza.csv")
+
+gaza_sample_df_summarized <- gaza_sample_df %>% 
                           rename(num_surveys = "# surveys") %>% 
-                          group_by(Stratification) %>% 
+                          group_by(strata) %>% 
                           summarise(num_surveys = sum(num_surveys))
+
+#gaza_sample_df_summarized <- write.csv(gaza_sample_df_summarized, sprintf("input/sample/gaza_sample_df_summarized_%s.csv", today()), row.names = FALSE)
 
@@
                         rename(num_surveys = "Survey") %>% 
-                        group_by(Location) %>% 
+                        group_by(strata) %>% 
                         summarise(num_surveys = sum(num_surveys))
 
-```
+#ej_sample_df_summarized <- write.csv(gaza_sample_df_summarized, sprintf("input/sample/ej_sample_df_summarized_%s.csv", today()), row.names = FALSE)
 
-```{r}
+############ add full strata
+######NOTE ::: CHANGE THE OSLO AREA TO REFLECT THE TOOL, A, B, C
+df <- df %>%
+  mutate(across(everything(), as.character)) %>%
+  mutate(strata =
+           case_when(location == "west_bank" & (oslo_area == "area_a" | oslo_area == "area_b") ~ "Area_AB",
+                     location == "west_bank" & oslo_area == "area_c" ~ paste(hh_location_wb, oslo_area, sep = "_"),
+                     location == "gaza" ~ hh_location_gaza,
+                     location == "ej"~ "East_Jerusalem",
+                     TRUE  ~  'H2'))
+
 ##########################################################################################
@@
 
-```
-
-```{r}
 ########################################################################################
@@
         line = list(color = 'rgb(205, 12, 24)', width = 4))
+survey_method_graph
 # interview_method Wide format
@@
                                             values_from = Number_of_interviews,
-                                            values_fill = list(Number_of_interviews = 0))%>% 
-  dplyr::select(Location, `Face to Face` = in_person, Phone = remote )
+                                            values_fill = list(Number_of_interviews = 0))
 
 interview_method_wide
-```
-```{r}
 ### Interview method Westbank
@@
 
-survey_method_graph_wb
-```
+interview_method_wide_wb
 
-```{r}
 ### Interview method Gaza
@@
 interview_method_wide_gaza
-```
-```{r}
+
 ### Interview method East Jerusalem
@@
 
+## Tracking by Location:: West Bank
+
+westbank_sample_inperson <- westbank_sample_df_summarized %>% 
+                          dplyr::select(strata, Sample = num_surveys)
+westbank_sample_inperson
+
+westbank_tracking_inperson <- df %>% 
+                              dplyr::filter(dc_method == "in_person" & location == "west_bank" | location == "H2") %>% 
+                              dplyr::group_by(strata) %>% 
+                              dplyr::summarise(Submissions = n(),
+                              Short_intv = sum(time_validity == "Deleted", na.rm = T),
+                              Deleted = sum(deleted == "yes", na.rm = T),
+                              Accepted = sum(deleted == "no", na.rm = T)
+                              )
+westbank_tracking_inperson
+
+westbank_tracking_merged_in_person <- left_join(westbank_sample_inperson, westbank_tracking_inperson, by = "strata") %>% 
+  mutate(
+    Remaining =  case_when(
+      is.na(Accepted) ~ Sample,
+      TRUE ~ (Accepted - Sample) * -1
+    )
+  )
+func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
+sumrow_in_person <- as.data.frame(lapply(westbank_tracking_merged_in_person, func))
+sumrow_in_person
+westbank_tracking_merged_in_person <- rbind(westbank_tracking_merged_in_person, sumrow_in_person ) %>%
+  mutate_all(
+    funs(replace_na(.,0)))
+westbank_tracking_merged_in_person
+########################################################################################
+
+########################################################################################
+
+## Tracking by Location:: Gaza
+
+gaza_sample_inperson <- gaza_sample_df_summarized %>% 
+                          dplyr::select(strata, Sample = num_surveys)
+gaza_sample_inperson
+
+gaza_tracking_inperson <- df %>% 
+                              dplyr::filter(dc_method == "in_person" & location == "gaza") %>% 
+                              dplyr::group_by(strata) %>% 
+                              dplyr::summarise(Submissions = n(),
+                              Short_intv = sum(time_validity == "Deleted", na.rm = T),
+                              Deleted = sum(deleted == "yes", na.rm = T),
+                              Accepted = sum(deleted == "no", na.rm = T)
+                              )
+gaza_tracking_inperson
+
+gaza_tracking_merged_in_person <- left_join(gaza_sample_inperson, gaza_tracking_inperson, by = "strata") %>% 
+  mutate(
+    Remaining =  case_when(
+      is.na(Accepted) ~ Sample,
+      TRUE ~ (Accepted - Sample) * -1
+    )
+  )
+func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
+gaza_sumrow_in_person <- as.data.frame(lapply(gaza_tracking_merged_in_person, func))
+gaza_sumrow_in_person
+gaza_tracking_merged_in_person <- rbind(gaza_tracking_merged_in_person, gaza_sumrow_in_person ) %>%
+  mutate_all(
+    funs(replace_na(.,0)))
+gaza_tracking_merged_in_person
+
+## Tracking by Location:: East Jerusalem
+
+EJ_sample_inperson <- ej_summarized_sample %>% 
+                          dplyr::select(strata, Sample = num_surveys)
+EJ_sample_inperson
+
+EJ_tracking_inperson <- df %>% 
+                              dplyr::filter(dc_method == "in_person" & location == "ej") %>% 
+                              dplyr::group_by(strata) %>% 
+                              dplyr::summarise(Submissions = n(),
+                              Short_intv = sum(time_validity == "Deleted", na.rm = T),
+                              Deleted = sum(deleted == "yes", na.rm = T),
+                              Accepted = sum(deleted == "no", na.rm = T)
+                              )
+EJ_tracking_inperson
+
+EJ_tracking_merged_in_person <- left_join(EJ_sample_inperson, EJ_tracking_inperson, by = "strata") %>% 
+  mutate(
+    Remaining =  case_when(
+      is.na(Accepted) ~ Sample,
+      TRUE ~ (Accepted - Sample) * -1
+    )
+  )
+func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
+EJ_sumrow_in_person <- as.data.frame(lapply(EJ_tracking_merged_in_person, func))
+EJ_sumrow_in_person
+EJ_tracking_merged_in_person <- rbind(EJ_tracking_merged_in_person, EJ_sumrow_in_person ) %>%
+  mutate_all(
+    funs(replace_na(.,0)))
+EJ_tracking_merged_in_person
+
+########################################################################################
+# Started before date of data collection
+started_before <- df %>% 
+  filter(today < assessment_start_date) %>% 
+  dplyr::select(Date = today,
+         Enumerator = enumerator_num,
+         Location = location)
+started_before
+
+# Enumerator productivity
+
+enumerator_productivity <- df %>% 
+  filter(df$consent == "yes") %>% 
+  group_by(Date = today, Enumerator = enumerator_num) %>% 
+  summarise(Interviews = n())
+
+enumerator_productivity_many <- enumerator_productivity %>% 
+  dplyr::filter(Interviews > max_interv)
+
+enumerator_productivity_less <- enumerator_productivity %>% 
+  dplyr::filter(Interviews < 3)
+
+enumerator_productivity_final <- rbind(enumerator_productivity_many, enumerator_productivity_less)%>% 
+  arrange(desc(Date) )
+
+# Enumerator per survey status
+
+enumer_per_survey_status <- df %>% 
+  filter(df$consent == "yes") %>% 
+  group_by(Date = today, Enumerator = enumerator_num) %>% 
+  summarise(Accepted = sum(time_validity != "Deleted", na.rm = T),
+            Deleted = sum(time_validity == "Deleted", na.rm = T )
+  )
+enumer_per_survey_status
+
+# Survey status per day
+
+survey_status_per_day <- df %>% 
+    filter(df$consent == "yes") %>% 
+  group_by(Date = today) %>% 
+  summarise(Accepted = sum(time_validity != "Deleted", na.rm = T),
+            Deleted = sum(time_validity == "Deleted", na.rm = T )
+  )
+survey_status_per_day
+
+# survey length by enumerator
+
+survey_length <- df %>% 
+    filter(df$consent == "yes") %>% 
+  group_by(Enumerator = enumerator_num) %>% 
+  dplyr::summarise(
+    Median_duration = round(median(as.numeric(df$interview_duration), na.rm = T),0)
+  ) %>% 
+  arrange(desc(Median_duration) )
+
+overall_survey_median <- round(median(as.numeric(df$interview_duration), na.rm = T),0)
+
+survey_length$Overall_median <-  overall_survey_median
+
+# Enumerator with short interv duration
+short_interviews_by_enum <- df %>% 
+  filter(df$consent == "yes" ) %>% 
+  dplyr::filter(interview_duration < time_limit & today > "2021-06-16") %>%
+
+  dplyr::select(Date = today, 
+                Enumerator = enumerator_num, 
+                Location = location,
+                Duration =  interview_duration,
+                Interview_Type = dc_method
+  ) %>% mutate(
+    Duration = round(as.numeric(Duration),0),
+  ) %>% 
+  arrange(desc(Date) )
+short_interviews_by_enum
 ```
+
+<center> **Data Collection Monitoring Report** </center>
+
+# {.tabset}
+
+***
+## Progress Statistics
+
+<center>**Number surveys per day of data collection** </center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+kable(survey_status_per_day)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+<center>**Interview Method - Completed Interviews**</center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+
+kable(interview_method_wide)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+***
+
+## Enumerator Productivity
+
+<center>**Number of surveys per day by enumerator** </center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+
+DT::datatable(enumer_per_survey_status,
+              options = list(
+                  pageLength = 2000,
+                  dom = 'ft'
+                )
+  ) %>% 
+  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
+  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold')
+
+```
+
+## General Checks
+
+<center>**surveys collected in under `r time_limit` minutes - last 7 days** </center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+kable(short_interviews_by_enum)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+
+***
+
+<center>**Surveyors with very low or high productivity** </center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+kable(enumerator_productivity_final)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+
+***
+
+<center>**Median interview duration by enumerator** </center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+kable(survey_length)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+<center>**Surveys made before the first day of data collection (**`r assessment_start_date`**)**</center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+kable(started_before)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+
+***
+
+## West Bank Interviews Tracking
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+DT::datatable(westbank_tracking_merged_in_person,
+              options = list(
+                  pageLength = 130,
+                  dom = 'ft'
+                )
+              ) %>% 
+  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
+  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>% 
+  DT::formatStyle('Short_intv',  color = 'red', fontWeight = 'bold') %>%
+  DT::formatStyle('Remaining', fontWeight = 'bold')
+```
+
+## Gaza Interviews Tracking
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+DT::datatable(gaza_tracking_merged_in_person,
+              options = list(
+                  pageLength = 130,
+                  dom = 'ft'
+                )
+              ) %>% 
+  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
+  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>% 
+  DT::formatStyle('Short_intv',  color = 'red', fontWeight = 'bold') %>%
+  DT::formatStyle('Remaining', fontWeight = 'bold')
+```
+
+## East Jerusalem Interviews Tracking
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+DT::datatable(EJ_tracking_merged_in_person,
+              options = list(
+                  pageLength = 130,
+                  dom = 'ft'
+                )
+              ) %>% 
+  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
+  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>% 
+  DT::formatStyle('Short_intv',  color = 'red', fontWeight = 'bold') %>%
+  DT::formatStyle('Remaining', fontWeight = 'bold')
+```

### 2021-06-28 MSNA_2021_Monitoring_report.Rmd
data cleaning update

@@
 library(Hmisc)
+library(rsconnect)
 source("functions/audit_function_full.R")

### 2021-06-28 data_cleaning_script.R

@@ -18,11 +18,12 @@ assessment_start_date <- as.Date("2021-06-16")
 
 # set min time and max # interviews per day
 
-time_limit <- 15
-flag_time_limit <- 30
+time_limit <- 10
+flag_time_limit <- 20
 max_interv <- 10
 
 df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "MSNA_I_2021")
+      
 
 ###########################################################################################################
 # time check from audit files
@@ -35,8 +36,8 @@ df <- time_check(df, time_limit)
 df <- df %>% 
   mutate(time_validity = case_when(interview_duration < flag_time_limit & 
                                      interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))
-df_raw <- df
-write.xlsx(df_raw, (file = sprintf("output/df_raw_%s.xlsx", today())))
+
+
 
 ###########################################################################################################
 df$time_validity
@@ -46,15 +47,34 @@ df$time_validity
 # when survey does not continue to hh member calculation, these surveys are not valid
 
 df <- df %>% 
-  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
-                                  TRUE ~ "no"))
+  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",TRUE ~ "no"),
+         uuid = `_uuid`,
+         X_uuid = uuid)
+
+
 df$not_eligible
+
+
 # import loop data
-indiv_df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "member")
+indiv_df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "member") %>% 
+            mutate(uuid = `_submission__uuid`,
+                   X_submission__uuid = uuid)
 
-indiv_df <- indiv_df %>%
-            mutate('_uuid' = '_submission__uuid')
+############ add full strata
+######NOTE ::: CHANGE THE OSLO AREA TO REFLECT THE TOOL, A, B, C
+df <- df %>%
+  mutate(across(everything(), as.character)) %>%
+  mutate(strata =
[…]

### 2021-06-28 MSNA_2021_Monitoring_report.Rmd
data cleaning update
Data cleaning update
Time limit changes

@@
 
-assessment_start_date <- as.Date("2021-06-16")
+assessment_start_date <- as.Date("2021-06-15")
 
@@
 
-time_limit <- 15
-flag_time_limit <- 30
+time_limit <- 10
+flag_time_limit <- 20
 max_interv <- 10
@@
   mutate(strata =
-           case_when(location == "west_bank" & (oslo_area == "area_a" | oslo_area == "area_b") ~ "Area_AB",
-                     location == "west_bank" & oslo_area == "area_c" ~ paste(hh_location_wb, oslo_area, sep = "_"),
+           case_when(location == "west_bank" & (oslo_area == "A" | oslo_area == "B") ~ "Area_AB",
+                     location == "west_bank" & oslo_area == "C" ~ paste(hh_location_wb, oslo_area, sep = "_"),
                      location == "gaza" ~ hh_location_gaza,
@@
 enumerator_productivity_final <- rbind(enumerator_productivity_many, enumerator_productivity_less)%>% 
-  arrange(desc(Date) )
+  dplyr::select(Enumerator, Interviews) %>% 
+  arrange(desc(Enumerator))
 
@@
   filter(df$consent == "yes" ) %>% 
-  dplyr::filter(interview_duration < time_limit & today > "2021-06-16") %>%
+  dplyr::filter(interview_duration < time_limit & today > "2021-06-15") %>%
 
@@
 ```
-<center>**Interview Method - Completed Interviews**</center> </br>
+<center>**Completed Interviews**</center> </br>
 

### 2021-06-30 MSNA_2021_Monitoring_report.Rmd
update on the cleaning scripts

@@
 
+survey_len <- df %>% 
+  filter(consent == "yes" & enumerator_num == "1") %>% 
+  dplyr::select(interview_duration)
 # survey length by enumerator
-
 survey_length <- df %>% 
@@
   group_by(Enumerator = enumerator_num) %>% 
-  dplyr::summarise(
-    Median_duration = round(median(as.numeric(df$interview_duration), na.rm = T),0)
-  ) %>% 
-  arrange(desc(Median_duration) )
+ summarise(
+    Median_duration = round(median(as.numeric(interview_duration), na.rm = T),0)
+  )%>% 
+  dplyr::arrange(desc(Median_duration) )
 
@@
 short_interviews_by_enum <- df %>% 
-  filter(df$consent == "yes" ) %>% 
+  dplyr::filter(df$consent == "yes" ) %>% 
   dplyr::filter(interview_duration < time_limit & today > "2021-06-15") %>%
@@
 
+## Productivity
+
+<center>**Surveyors with very low or high productivity** </center> </br>
+
+```{r eval=TRUE, echo=FALSE, results='asis'}
+kable(enumerator_productivity_final)%>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
+```
+
 ## General Checks
@@
 kable(short_interviews_by_enum)%>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
-```
-
-***
-
-<center>**Surveyors with very low or high productivity** </center> </br>
-
-```{r eval=TRUE, echo=FALSE, results='asis'}
-kable(enumerator_productivity_final)%>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)

### 2021-06-30 data_cleaning_script.R
Add GPS strata check and distance to settlement

@@ -1,3 +1,4 @@
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 library(dplyr)
 library(lubridate)
 library(readxl)
@@ -8,6 +9,8 @@ library(openxlsx)
 library(sf)
 library(raster)
 library(Hmisc)
+library(leaflet)
+library(htmlwidgets)
 source("functions/audit_function_full.R")
 source("functions/function_handler.R")
 
@@ -24,6 +27,92 @@ max_interv <- 10
 
 df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "MSNA_I_2021")
       
+###########################################################################################################
+# [GPS] STRATA CHECK
+###########################################################################################################
+# load shape files
+gov_WB <- st_read("input/shapes/Governorates_WB/Governorates_WB.shp") %>% st_transform(crs = 4326)
+oslo <- st_read("input/shapes/Oslo_EJ_NML/Oslo_EJ_NML.shp") %>% st_transform(crs = 4326)
+# load settlements GDB file
+dir.settlements <- "input/shapes/IsraeliSettlements.gdb/"
+layers <- st_layers(dir.settlements)
+settlements_outer <- st_transform(st_read(dir.settlements, layer=layers$name[1]), crs = 4326)
+settlements_builtup <- st_transform(st_read(dir.settlements, layer=layers$name[2]), crs = 4326)
+# merge outer and builup layer
+settlements <- rbind(dplyr::select(settlements_builtup, Name_Eng) %>% rename(Name=Name_Eng),
+                     dplyr::select(settlements_outer, Name))
+settlements <- st_cast(st_union(settlements), "POLYGON")
+
+# keep only samples with GPS coordinates and convert dataframe to sf
+df_wb_sf <- df %>% 
+  filter(location=="west_bank" & !is.na(gpslocation)) %>% 
+  st_as_sf(coords=c("_gpslocation_longitude", "_gpslocation_latitude"), crs = 4326)
+
+# add governorate and oslo information based on GPS coordinates
+df_wb_sf <- st_join(df_wb_sf, dplyr::select(gov_WB, GOVERNORAT))
+df_wb_sf <- st_join(df_wb_sf, dplyr::select(oslo, CLASS))
+# reformat governorate and oslo area
+df_wb_sf <- df_wb_sf %>% 
+  mutate(gps.governorate=tolower(GOVERNORAT),
[…]

### 2021-07-01 data_cleaning_script.R
Minor changes to spatial check

@@ -66,7 +66,7 @@ df_wb_sf_issues <- filter(df_wb_sf, hh_location_wb!=gps.governorate)
 View(dplyr::select(df_wb_sf_issues, hh_location_wb, oslo_area, gps.governorate, gps.oslo.area))
 map <- leaflet() %>% 
   addPolygons(data=gov_WB, color = "#0080FF", weight = 1, fillOpacity=0.2, opacity = 0.8, label = gov_WB$GOVERNORAT) %>%
-  addCircles(data = df_wb_sf_issues, stroke = F, fill = T, fillOpacity = 1, radius = 100, fillColor="#FF0000",
+  addCircles(data = df_wb_sf_issues, stroke = F, fill = T, fillOpacity = 1, radius = 50, fillColor="#FF0000",
              label=paste0(df_wb_sf_issues$`_index`, ": ", df_wb_sf_issues$hh_location_wb, "-", df_wb_sf_issues$oslo_area)) %>%
   addTiles()
 saveWidget(map, file="samples_gov.html")
@@ -78,16 +78,22 @@ map <- leaflet() %>%
   addPolygons(data=oslo, 
               color = c("#0080FF", "#EE00FF", "#33FF00", "#FF9900", "#00ffff", "#ff0000", "#0000ff"), 
               weight = 1, fillOpacity=0.2, opacity = 0.8, label = oslo$CLASS) %>%
-  addCircles(data = df_wb_sf_issues, stroke = F, fill = T, fillOpacity = 1, radius = 100, fillColor="#FF0000",
+  addCircles(data = df_wb_sf_issues, stroke = F, fill = T, fillOpacity = 1, radius = 50, fillColor="#FF0000",
              label=paste0(df_wb_sf_issues$`_index`, ": ", df_wb_sf_issues$hh_location_wb, "-", df_wb_sf_issues$oslo_area)) %>%
   addTiles()
 saveWidget(map, file="samples_oslo.html")
 
 # generate cleaning log
+issue1 <- "Sample GPS location is not within the specified governorate and Oslo area."
+issue2 <- "Sample GPS location is not within the specified governorate."
+issue3 <- "Sample GPS location is not within the specified Oslo area."
 df_wb_sf_issues <- df_wb_sf %>% 
   dplyr::filter(hh_location_wb!=gps.governorate | oslo_area!=gps.oslo.area) %>% 
-  dplyr::select("_uuid", hh_location_wb, gps.governorate, oslo_area, gps.oslo.area) %>% 
[…]

### 2021-07-04 MSNA_2021_Monitoring_report.Rmd
data cleaning update
update on the dashboard.

@@
 
-# df <- time_check(df, time_limit)
+df <- time_check(df, time_limit)
 df <- df %>% 
@@
 ###########################################################################################################
+df$time_validity
 
@@
 df <- df %>% 
-  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
+  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",TRUE ~ "no"),
+         uuid = `_uuid`,
+         X_uuid = uuid)
+
+df$not_eligible
+
+############ add full strata
+######NOTE ::: CHANGE THE OSLO AREA TO REFLECT THE TOOL, A, B, C
+df <- df %>%
+  mutate(across(everything(), as.character)) %>%
+  mutate(strata =
+           case_when(location == "west_bank" & (oslo_area == "area_a" | oslo_area == "area_b") ~ "Area_AB",
+                     location == "west_bank" & oslo_area == "area_c" ~ paste(hh_location_wb, oslo_area, sep = "_"),
+                     location == "gaza" ~ hh_location_gaza,
+                     location == "ej"~ "East_Jerusalem",
+                     TRUE  ~  'H2'))
+
+#### df after the time check
+#df_raw <- df
+#write.xlsx(df_raw, (file = sprintf("output/df_raw_%s.xlsx", today())))
+
+##########################################################################################
+# Deleted interviews column
+df <- df %>% 
+  mutate(
+    deleted = case_when(
+      time_validity == "Deleted" | consent == "no" | not_eligible == "yes" ~ "yes",
       TRUE ~ "no"))
-
-# remove ineligible surveys
-df %<>% filter(consent == "yes" & not_eligible == "no")
-
+df$deleted
 ########## SAMPLE FRAMES ########################
@@
 westbank_sample_inperson <- westbank_sample_df_summarized %>% 
-                          dplyr::select(strata, Sample = num_surveys)
+                          dplyr::select(strata, Max_Surveys = num_surveys)
 westbank_sample_inperson
@@
     Remaining =  case_when(
-      is.na(Accepted) ~ Sample,
-      TRUE ~ (Accepted - Sample) * -1
+      is.na(Accepted) ~ Max_Surveys,
+      TRUE ~ (Accepted - Max_Surveys) * -1
     )
@@
 westbank_tracking_merged_in_person <- rbind(westbank_tracking_merged_in_person, sumrow_in_person ) %>%
-  mutate_all(
-    funs(replace_na(.,0)))
-westbank_tracking_merged_in_person
+  mutate_all(funs(replace_na(.,0))) %>% 
+  dplyr::mutate(Min_Surveys = round(Max_Surveys*0.85,0))
+westbank_tracking_merged_in_person <- westbank_tracking_merged_in_person %>% 
+          relocate(c("Min_Surveys"), .before = "Max_Surveys")
 ########################################################################################
@@
 gaza_sample_inperson <- gaza_sample_df_summarized %>% 
-                          dplyr::select(strata, Sample = num_surveys)
+                          dplyr::select(strata, Max_Surveys = num_surveys)
 gaza_sample_inperson
@@
   mutate_all(
-    funs(replace_na(.,0)))
+    funs(replace_na(.,0))) %>% 
+dplyr::mutate(Min_Surveys = round(Max_Surveys*0.90,0))
+gaza_tracking_merged_in_person <- gaza_tracking_merged_in_person %>% 
+          relocate(c("Min_Surveys"), .before = "Max_Surveys")
 gaza_tracking_merged_in_person
@@
 EJ_sample_inperson <- ej_summarized_sample %>% 
-                          dplyr::select(strata, Sample = num_surveys)
+                          dplyr::select(strata, Max_Surveys = num_surveys)
 EJ_sample_inperson
@@
   mutate_all(
-    funs(replace_na(.,0)))
+    funs(replace_na(.,0))) %>% 
+dplyr::mutate(Min_Surveys = round(Max_Surveys*0.85,0))
+EJ_tracking_merged_in_person <- EJ_tracking_merged_in_person %>% 
+          relocate(c("Min_Surveys"), .before = "Max_Surveys")
 EJ_tracking_merged_in_person

### 2021-07-04 MSNA_2021_Monitoring_report.Rmd
Update on the dashboard
Update on the monitoring script.

@@
 
-interview_method_wide
+interview_method_wide <- rename(interview_method_wide, "Number_of_interviews" = "in_person")
 ### Interview method Westbank
@@
 
+enum_productivity <- df %>% 
+  filter(df$consent == "yes") %>% 
+  group_by(Enumerator = enumerator_num) %>% 
+  summarise(Interviews = n()) %>% 
+  arrange(desc(Interviews), .by_group = T)
+
 # Enumerator per survey status
@@
 
-## Enumerator Productivity
+## Enumerator Progress
 
@@
 
-## Productivity
+##  Enumerator Productivity
 
@@
 ```{r eval=TRUE, echo=FALSE, results='asis'}
-kable(enumerator_productivity_final)%>%
+kable(enum_productivity)%>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)

### 2021-07-04 Recoding.R
Create Recoding.R
Binary Recoding

@@ -1,0 +1,84 @@
+
+library(dplyr)
+library(readxl)
+library(Hmisc)
+
+
+
+r <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "MSNA_I_2021")
+
+##of interviews conducted with head of household
+r$hh1 <- ifelse(r$hhh_r == "yes", 1,0)
+r$hh1
+table(r$hh1)
+prop.table(table(r$hh1))
+
+##% of interviews conducted with male or female participants
+
+
+
+
+
+
+## households that can access a functional basic and secondary school within a 30min walk from dwellings
+
+r$E11 <- ifelse(r$primary_school_distance %in% c("less_15", "less_30") &
+                   r$secondary_school_distance %in% c("less_15", "less_30"),1,0)
+table(r$E11)
+prop.table(table(r$E11)) ###0.8761062
+
+##HHs whose monthly income has decreased as a result of COVID-19
+r$L2 <- ifelse(r$income_change_covid == "yes" ,1,0)
+
+table(r$L2)
+prop.table(table(r$L2))
+
+##HHs with debt value > 30000
+
+r$L4 <- ifelse(r$how_much_debt > 30000, 1,0)
+
+table(r$L4)
+prop.table(table(r$L4))
+
+## HH with at least one adult (18+) unemployed and seeking work
+r$L9 <- ifelse(r$unemployed_adults > 0, 1,0)
+r$L9 
+table(r$L9)
+prop.table(table(r$L9))
+
+##HH reporting members losing jobs permanently or temporarily as a result of the Covid-19 outbreak
+r$L12 <- ifelse(r$covid_loss_job == "yes", 1,0)
+r$L12
+table(r$L12)
+prop.table(table(r$L12))
+
+##AD1  ==  % of HHs who have received aid that are reporting that 
+## they are unsatisfied with the quantity of the received aid
+r$AD1 <- case_when( r$`aid_not_satisfied/quantity_not_enough` == "1" ~ 1,
+                    r$`aid_not_satisfied/quantity_not_enough` == "0" ~ 0,
+                    TRUE ~ NA_real_)
+r$AD1
+table(r$AD1)
+prop.table(table(r$AD1))
+
+##AD2  ==  % of HHs who are renting an apartment that report being 
+##at risk of eviction
+
[…]

### 2021-07-04 Recoding.R
Updated Recording scripts

@@ -8,17 +8,81 @@ library(Hmisc)
 r <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "MSNA_I_2021")
 
 ##of interviews conducted with head of household
-r$hh1 <- ifelse(r$hhh_r == "yes", 1,0)
+r$hh1 <- ifelse(r$hhh_r == "yes", 1, 0)
 r$hh1
 table(r$hh1)
 prop.table(table(r$hh1))
 
 ##% of interviews conducted with male or female participants
+r$hh5 <- ifelse(r$gender_respondent == "female", 1, 0)
+r$hh5
+table(r$hh5)
+prop.table(table(r$hh5))
 
+##% of households by sex of household head
+r$hh6 <- case_when( r$sex_head_hh == "female" ~ 1,
+                    r$sex_head_hh == "male" ~ 0,
+                    TRUE ~ NA_real_)
+r$hh6
+table(r$hh6)
+prop.table(table(r$hh6))
 
+##% of interviews conducted according to refugee status of household
 
+r$hh8 <- ifelse(r$refugee_status == "yes", 1, 0)
+r$hh8
+table(r$hh8)
+prop.table(table(r$hh8))
 
+##% of households with at least one member pregnant or lactating
 
+r$hh10 <- ifelse(r$preg_lactating == "yes", 1, 0)
+r$hh10 
+table(r$hh10)
+prop.table(table(r$hh10))
+
+##% of households with at least one member with a chronic disease
+r$chronic_illness
+
+r$hh12 <- ifelse(r$chronic_illness == "yes", 1, 0)
+table(r$hh12)
+prop.table(table(r$hh12))
+
+##% of HHs displaced as a result of the most recent conflict (starting on the 1st of May 2021)
+r$permanent_location
+
+r$hhd1 <- case_when(r$permanent_location == "no" ~ 1,
+                    r$permanent_location %in% c("yes", "do_not_know", "decline_to_answer") ~ 0,
+                    TRUE ~ NA_real_)
+r$hhd1
+table(r$hhd1)
+prop.table(table(r$hhd1))
+
+##% of HHs that have been displaced as a result of the recent conflict, 
+##but have since returned to their previous location
+r$displacement_status
+
+r$hhd2 <- case_when(r$displacement_status == "yes" ~ 1,
[…]
